Convex Surrogates via Polyhedral Losses

### 2019-02-02 cvx-fin.tex
comment

  \item \cite{ramaswamy2018consistent} \jessie{Originally in 2014... new version in 2018.} is the first paper, to our knowledge to prove bounds on the elicitation complexity of the abstain property.
  They shouw that the abstain property with $\alpha = 1/2$ can be elicited by a convex surrogate in $\ceil*{\log_2 n}$ dimensions.
  However, it remains unknown if this bound is tight, although in Conjecture~\ref{conj:abstain-tight}, we conjecture that their bound is tight, at least from the perspective from embedding.
  If true, then we will need new approaches in order to indirectly elicit the abstain property by a convex surrogate.
  \item \cite{agarwal2015consistent} introduces the notion of a \emph{calibrated property}, which is very similar to our ``embedded property'' that we actually elicit by a convex surrogate in lieu of directly eliciting a finite (i.e. classification, ranking) property.
  However, they do not think of properties as set-valued, leading to a less rigorous treatment and understanding of the link.
  Most of their results focus on linear properties \jessie{is there a relationship between linear and orderable properties?}

@@

\begin{definition}[Elicits]
  A loss $\ell:\R\to\reals^\Y_+$, \emph{elicits} a property $\gamma:\simplex \toto \R$ if for all $p \in \simplex$,
  \begin{equation}
  \Gamma(p) = \argmin_{r \in \R} \inprod{p}{L(r)}~.
  \end{equation}
\end{definition}
This terminology comes from the information elicitation literature, in which a report $r$ is elicited from some forecaster by scoring her with a loss on the observed outcome $y$; she tries to minimize expected loss.

@@

  Applying the same argument iteratively, we know that if $v_c$ is the second-longest normal, in order for $(V, T_c)$ to be tight, we must observe $\theta_{c-1, c} > 60^o$ and $\theta_{c,c+1} > 60^o$.
  In fact, this argument must hold for each $\theta_j, j+1$.
  Additionally, we see for all $j$, that $\theta_{j,j+2} > 120^o$.
  However, since we know $\sum_{i=1}^6 \theta_{i,i+2} = 720$, and thus there must be some $\theta_{i,i+2} \leq 120$, yielding a contradiction.

>>>>

  \item \cite{ramaswamy2018consistent} \jessie{Originally in 2014... new version in 2018.} is the first paper, to our knowledge to prove bounds on the elicitation complexity of the abstain property.
  They show that the abstain property with $\alpha = 1/2$ can be elicited by a convex surrogate in $\ceil*{\log_2 n}$ dimensions.
  However, it remains unknown if this bound is tight, although in Conjecture~\ref{conj:abstain-tight}, we conjecture that their bound is tight, at least from the perspective from embedding.
  If true, then we will need new approaches in order to indirectly elicit the abstain property by a convex surrogate.
  \item \cite{agarwal2015consistent} introduces the notion of a \emph{calibrated property}, which is very similar to our ``embedded property'' that we actually elicit by a convex surrogate in lieu of directly eliciting a finite (i.e. classification, ranking) property.
  However, they do not think of properties as set-valued, leading to a less rigorous treatment and understanding of the link.
  Most of their results focus on linear properties \jessie{is there a relationship between linear and orderable properties?}

@@

\begin{definition}[Elicits]
  A loss $\ell:\R\to\reals^\Y_+$, \emph{elicits} a property $\gamma:\simplex \toto \R$ if for all $p \in \simplex$,
  \begin{equation}
  \Gamma(p) = \argmin_{r \in \R} \inprod{p}{L(r)}~.
  \end{equation}
  \bo{add $\gamma[\ell]$ notation}
\end{definition}
This terminology comes from the information elicitation literature, in which a report $r$ is elicited from some forecaster by scoring her with a loss on the observed outcome $y$; she tries to minimize expected loss.

@@

  Applying the same argument iteratively, we know that if $v_c$ is the second-longest normal, in order for $(V, T_c)$ to be tight, we must observe $\theta_{j-1, j} > 60^o$ and $\theta_{j,j+1} > 60^o$.
  In fact, this argument must hold for each $\theta_j, j+1$.
  Additionally, we see for all $j$, that $\theta_{j,j+2} > 120^o$.
  However, since we know $\sum_{i=1}^6 \theta_{i,i+2} = 720$, and thus there must be some $\theta_{i,i+2} \leq 120$, yielding a contradiction.
